---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# distancetoland

The goal of distancetoland is to provide an easy lookup for the "distance to coastline" for longitude and latitude coordinates. 

## Installation

The distancetocoast package may be installed from Github using devtools. 

```{r,eval=FALSE}
devtools::install_github("AustralianAntarcticDivision/distancetocoast")
```


## Example

There is an in-built data set, in `raster` format. The raster package
includes an `extract` function which will look up a cell value at 
a given longitude and latitude location. 

This value is the distance to the coastline from the centre of the cell. 
```{r example}
library(distancetocoast)
library(raster)
## beware of clashing with tidyr::extract
raster::extract(distance_to_coastline_lowres, cbind(147, -42))
```

This is a very approximate value, and it will depend on the content and quality of the coastline data used, on the resolution of the grid itself, some un-quantified local distortions due to coordinate transformations and discretization, and may not be accurate for some applications. 

This grid was created by process it in tiles, reprojecting the coastline and the grid pixel centres to a local Lambert Azimuthal Equi-distant projection and calculating shortest Cartesian distance to the coastline coordinate in that projection. (We used the `nabor` package). 

```{r}
plot(distance_to_coastline_lowres, col = viridis::viridis(64))
plot(rnaturalearth::ne_coastline(), add = TRUE)
```
The in-built data can be interrogated directly for its properties. 

```{r}
## resolution (cell size in native coordinates)
raster::res(distance_to_coastline_lowres)

## dimensions (number of columns and rows)
dim(distance_to_coastline_lowres)

## the extent, in native coordinates
raster::extent(distance_to_coastline_lowres)

## the "CRS", coordinate reference system (the map projection)
raster::projection(distance_to_coastline_lowres)

## the range of values (distance in metres)
cellStats(distance_to_coastline_lowres, min)
cellStats(distance_to_coastline_lowres, max)
```

All of this information may be seen in one step by using the print method. 

```{r}
distance_to_coastline_lowres
```

The distance values are currently 


See '/data-raw/' for the code used to produce this layer. 


## Development

We hope to add more data sets with a wider choice of methods so that an appropriate choice can be made for specific applications. 



Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

